Reconstructing Propositional Proofs in Type Theory

### 2017-12-17 paper/sections/type-theory.tex
added footer to review paper.

In~\eqref{eq:uh-definition}, the first two equations
call on arguments no structurally smaller.
For instance, in the first equation,
$$\fuh_{0} (φ₁ ⇒ (φ₂ ⇒ φ₃)) = \fuh_{0}~((φ₁ ∧ φ₂) ⇒ φ₃),$$
the function $\fuh_{0}$ calls on the  $(φ₁ ∧ φ₂) ⇒ φ₃$ argument in the right-hand side but this formula is not a subformula of $φ₁ ⇒ (φ₂ ⇒ φ₃)$.
Therefore, one way to translate $\fuh_{0}$ to type
theory is to define a new function using a bounded recursion.

@@

Therefore, we define in~\eqref{eq:uh-complexity} the complexity
measure function of $\fuh_{0}$ by assigning the number of steps to
finish for each pattern-matching case.
We have used the complexity measure definition for a formula defined in~\cite{Agudelo-Agudelo2017} to define other complexity measures
in this paper.

@@

We formalise the syntactical consequence relation of \CPL by an
inductive family \verb!_⊢_! with two indexes, a set of propositions (the
premises) and a proposition (the conclusion), that is, $Γ ⊢ φ$
represents that there is derivation with conclusion $φ : \Prop$ from
the set of premises $Γ : \List~\Prop$. We implemented
in~\cite{AgdaProp} the syntactical consequence relation in a similar
way as it was presented in~\cite{Altenkirch2015}. For that reason, we
have included structural rules like \emph{weaken}, formation and
elimination rules for connectives and the PEM axiom as the valid
inference rules in Fig.~\ref{fig:CPL-inference-rules}.

>>>>

In~\eqref{eq:uh-definition} is a definition no structurally recursive.

% TODO
% , the first two equations
% call on arguments no structurally smaller.
% For instance, in the first equation,
% $$\fuh_{0} (φ₁ ⇒ (φ₂ ⇒ φ₃)) = \fuh_{0}~((φ₁ ∧ φ₂) ⇒ φ₃),$$
% the function $\fuh_{0}$ calls on the argument $(φ₁ ∧ φ₂) ⇒ φ₃$ argument. However, this formula is not a subformula of $φ₁ ⇒ (φ₂ ⇒ φ₃)$.

Therefore, one way to translate $\fuh_{0}$ to type
theory is to define a new function using a bounded recursion.

@@

Therefore, we define in~\eqref{eq:uh-complexity} the complexity
measure function of $\fuh_{0}$ by assigning the number of steps to
finish for each pattern-matching case.

% In this particular case,
% as we can see by the definition of the $\fuh_{0}$ function, the pattern-matching cases depend on the formula structure for implications. For example, when φ ≡ in the consequent when the input formula is an implication. For example, when the input formula
% is an implication like φ₁ ⇒ (φ₂ ∧ φ₃) then, the recursive calls
% are using only the consequent φ₂ ∧ φ₃, otherwise, if φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃) based on the cases of the function definition, we only need
% to take care of φ₃.

We have used the complexity measure definition for a formula defined in~\cite{Agudelo-Agudelo2017} to define other complexity measures
in this paper.

@@

We formalize the syntactical consequence relation of \CPL by an
inductive family \verb!_⊢_! with two indexes, a set of propositions (the
premises) and a proposition (the conclusion), that is, $Γ ⊢ φ$
represents that there is derivation with conclusion $φ : \Prop$ from
the set of premises $Γ : \List~\Prop$. We implemented
in~\cite{AgdaProp} the syntactical consequence relation in a similar
way as it was presented in~\cite{Altenkirch2015}. For that reason, we
have included structural rules like \emph{weaken}, formation and
elimination rules for connectives and the PEM axiom as the valid
inference rules in Fig.~\ref{fig:CPL-inference-rules}.
